Paper_Figure

### 2024-08-11 LMD-paper/paper_figure.Rmd
package_refine

---
title: "Paper_Figure"
author: "Ruiqi Li"
output: pdf_document
date: '2023-10-16'
---
# Load Data & Preprocess
```{r}
library("Seurat")
library("RColorBrewer")
library("dplyr")
library("patchwork")
library("ggplot2")
library("ggsignif")
source("LMD_function.R", echo = F)
dir.path0 = "/banach1/ruiqi/local_marker"
dir.path1 = "/banach1/ruiqi/Peggy_data/Peggy_scdata/240329_smom2"
figure_path = file.path(dir.path0, "LMD_data","figures")
dir.create(figure_path,recursive = TRUE)
setwd(figure_path)
```

# SupFig - Bone Marrow Cell Embedding
```{r}
dir.path <- file.path(dir.path0,"LMD_data")
consortium = "tabular_muris"
folder.path <- file.path(dir.path,consortium)
tissue_name = "marrow_facs"
tiss <- readRDS(file.path(folder.path,paste0(tissue_name,".rds")))
cell_label = tiss$cell_ontology_class
coldef = setNames(colorRampPalette(brewer.pal(12, "Paired"))(length(unique(cell_label))),unique(cell_label))
p1 = DimPlot(tiss, group.by = "cell_ontology_class",label = FALSE, cols = coldef) + guides(color = guide_legend(ncol = 1,override.aes = list(size = 3))) + labs(title = NULL)

@@

# Fig - Pipeline
```{r}
source("LMD_function.R", echo = F)
dir.path <- file.path(dir.path0,"LMD_data")
consortium = "tabular_muris"
folder.path <- file.path(dir.path,consortium)
tissue_name = "marrow_facs"
tiss <- readRDS(file.path(folder.path,paste0(tissue_name,".rds")))
W <- readRDS(file.path(folder.path,"intermediate_data",tissue_name,paste0(tissue_name,"_knn_graph.rds")))
res <- readRDS(file.path(folder.path,"intermediate_data",tissue_name,paste0(tissue_name,"_lmd_profile.rds")))
P_ls <- readRDS(file.path(folder.path,"intermediate_data",tissue_name,paste0(tissue_name,"_diffused_graph.rds")))
rho <- readRDS(file.path(folder.path,"intermediate_data",tissue_name,paste0(tissue_name,"_gene_distribution.rds")))
```
```{r}
# Plot knn graph
p = plot_knn_graph(affinity_m = W, layout = Embeddings(tiss[["tsne"]])) + NoLegend()
ggsave(filename = file.path(figure_path,"fig-pipeline1.png"), plot = p, width = 5, height = 5, dpi = 300)
```
```{r}
# Check Diffusion KL pattern for several genes
# good gene: Igll1,Fcnb # garbage marker: Fkbp1b, Tnks1bp1, Magi2,Uchl4
genes = c("Igll1","Tnks1bp1") 
# genes_label = c("localized","non_localized")
check_time = c(0,2^3,2^9,2^14)
p = Visualize_score_pattern(res$score_profile/res$score_profile$max_score0, genes = genes, add_point = check_time) + guides(linetype = "none")

@@

ggsave(filename = file.path(figure_path,"fig-pipeline2.png"), plot = p, width = 8, height = 5)
```
```{r}
# Check Gene Diffusion on Cell graph by time
pl = lapply(1:length(genes),function(i){
  gene = genes[i]
  FeaturePlot_diffusion(coord = Embeddings(tiss[["tsne"]]),init_state = rho[gene,,drop = FALSE],P_ls = P_ls,W = W,check_time = check_time,gene_name = NULL, gene_color = scales::hue_pal()(length(genes))[i])
})
p = as.ggplot(pl[[1]]) / as.ggplot(pl[[2]] & labs(title = NULL))
ggsave(filename = file.path(figure_path,"fig-pipeline3.png"), plot = p, width = 16, height = 8)
```

# Fig - the AUROC given the rank and the ground truth
```{r}
method_ls = c("lmd","haystack","hotspot","marcopolo","semi","wilcox_no_filter","hvg")
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v4","HVGs"),method_ls)
```
```{r}
dir.path <- dir.path0
consortium = "tabular_muris"
tissue_name = "marrow_facs"
folder.path = file.path(dir.path, "LMD_data","benchmark")
```
```{r}
# Define Full name
tissue_ls = list("tabular_muris" = c("marrow_facs","pancreas_facs","lung_facs"),
                 "azimuth" = c("human_kidney", "human_bone_marrow", "human_pancreas", "mouse_motor_cortex", "human_lung_hlca", "human_motor_cortex"))
consortium_full_name = c("tabular_muris" = "Tabular Muris","azimuth" = "Azimuth")
tissue_full_name = lapply(unlist(tissue_ls),function(i){
  tmp_name = 
  if(grepl("marrow",i)){tmp_name = "Bone Marrow"}
  else if(grepl("lung_hlca",i)){tmp_name = "Lung v2 (HLCA)"}
  else if(grepl("lung",i)){tmp_name = "Lung"}
  else if(grepl("pancreas",i)){tmp_name = "Pancreas"}
  else if(grepl("kidney",i)){tmp_name = "Kidney"}
  else if(grepl("motor_cortex",i)){tmp_name = "Motor Cortex"}
  else{tmp_name = NA}
  tmp_name
})
names(tissue_full_name) = unlist(tissue_ls)
tissue_full_name = unlist(lapply(1:length(tissue_full_name),function(i){
  ori_name = names(tissue_full_name)[i]
  if(grepl("_facs|mouse",ori_name)){
    tmp_name = paste0("Mouse-\n",tissue_full_name[i])
  }
  else if(grepl("human",ori_name)){
    tmp_name = paste0("Human-\n",tissue_full_name[i])
  }
  else{
    tmp_name = tissue_full_name[i]
  }
  tmp_name
}))
names(tissue_full_name) = unlist(tissue_ls)
```
```{r}
df_auc = do.call(rbind,
                lapply(1:length(tissue_ls),function(i){
                  df_all = NULL
                  for(j in tissue_ls[[i]]){
                    df = read.table(file.path(folder.path, names(tissue_ls)[i],paste0(j,"_auroc.csv")),header = TRUE)
                    df$'Tissue' = j
                    df_all = rbind(df_all,df)
                  }
                  df_all$'consortium' = names(tissue_ls)[i]
                  df_all}))
df_auc$Method = method_fullname[df_auc$Method]
df_auc = df_auc %>% filter(gt_set %in% c("CellMarkerDB","Top100"))
# Order Method based on mean AUROC
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("CellMarkerDB","Top100"))
levels(df_auc$gt_set) = c("Criterion1-\n CellMarkerDB","Criterion2-\n MaxFC")
df_auc$Tissue = tissue_full_name[df_auc$Tissue]
df_auc$consortium = consortium_full_name[df_auc$consortium]
df_auc$consortium = factor(df_auc$consortium, levels = consortium_full_name)
```
## Figure
```{r}
coldef = setNames(
  colorRampPalette(brewer.pal(8, "Set1"))(length(method_fullname)),
  method_fullname)

fig <- ggplot(df_auc, aes(x = Tissue, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") + facet_grid(gt_set~consortium, scales = 'free') +
  geom_text(aes(label = round(AUROC, 3)), position = position_dodge(width = 1), vjust = -0.25, size = 2.5, angle = 45) +
  labs(x = "Tissue", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method])

@@

ggsave(filename = file.path(figure_path,"fig-known_marker_comparison.png"), plot = fig, width = 12, height = 6)
```
## Table
```{r}
library("reshape2")
wide_data = df_auc; wide_data$AUROC = round(wide_data$AUROC,3)
wide_data <- reshape2::dcast(wide_data, gt_set + Tissue + consortium ~ Method, value.var = "AUROC")
colnames(wide_data)[1:3] = c("Criterion","Tissue","DataSource")
wide_data[,1:3] = wide_data[,3:1]; colnames(wide_data)[1:3]=colnames(wide_data)[3:1]
wide_data <- wide_data[order(wide_data$DataSource,wide_data$Tissue,wide_data$Criterion),]
wide_data[,1:3] = apply(wide_data[,1:3],2,function(x) gsub("[\n]|Criterion1-|Criterion2-","",x))
wide_data[,1:2] = apply(wide_data[,1:2],2,function(x) {x[duplicated(x)] = "";x})
wide_data$Tissue[17] = "Motor Cortex(Mouse)"
wide_data$Tissue[13] = "Motor Cortex(Human)"
wide_data$Tissue = gsub("Human-|Mouse-","",wide_data$Tissue)
# calculate average
avg_tmp = wide_data %>%
    group_by(Criterion) %>%
    summarize(across(3:(ncol(wide_data)-1), ~ round(mean(.x, na.rm = TRUE), 3)))
avg_tmp$DataSource = c("Average",""); avg_tmp$Tissue = "-"
wide_data = rbind(wide_data,avg_tmp)
bold_max <- function(vec) {
  max_val <- max(vec, na.rm = TRUE)
  vec = unlist(ifelse(vec == max_val, paste0("\\textbf{", vec, "}"), vec))
  return(vec)
}
wide_data[,4:ncol(wide_data)] = t(apply(wide_data[,4:ncol(wide_data)],1,bold_max))
wide_data[is.na(wide_data)] = "-"

write.csv(wide_data, file = file.path(folder.path,"AUROC_table.csv"), row.names = FALSE)
```
# SupFig-RunTime
```{r}
df_runtime = do.call(rbind,
                lapply(1:length(tissue_ls),function(i){
                  df_all = NULL
                  for(j in tissue_ls[[i]]){
                    df = read.table(file.path(folder.path, names(tissue_ls)[i],paste0(j,"_runtime.csv")),header = TRUE)
                    df$'Tissue' = j
                    df_all = rbind(df_all,df)
                  }
                  df_all$'consortium' = names(tissue_ls)[i]
                  df_all}))
df_runtime$Method = method_fullname[df_runtime$Method]
df_runtime$Tissue = tissue_full_name[df_runtime$Tissue]
df_runtime$consortium = consortium_full_name[df_runtime$consortium]
```
## Figure
```{r}
coldef = setNames(
  colorRampPalette(brewer.pal(8, "Set1"))(length(method_fullname)),
  method_fullname)

@@

# Fig - Gene Ranking Comparisons between LMD and Other Methods
```{r}
dir.path <- dir.path0
consortium = "tabular_muris"
tissue_name = "marrow_facs"
df_benchmark = read.table(file.path(dir.path, "LMD_data","benchmark", consortium, paste0(tissue_name,"_benchmark_rank_table.csv")),header = TRUE)
rownames(df_benchmark) = df_benchmark$gene
tiss = readRDS(file.path(dir.path, "LMD_data",consortium, paste0(tissue_name,".rds")))
method_vs = "lmd"
method_vs_set = c("wilcox_no_filter","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
# df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
#   paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
# })
g = c("Cd19","Naaa","Mogat2","Grina","Abca13","Zf12","Il2rb","Phgdh","Vpreb2","Fyb")
names(g) = rep(method_vs_set,each = 2)
pl = lapply(1:length(g),function(i){
  x = g[i]
  subtitle = sprintf("%s:%d, %s:%d",method_fullname[method_vs],df_label_all[x,method_vs],method_fullname[names(g)[i]],df_label_all[x,names(g)[i]])
  color_label = ifelse(df_label_all[x,method_vs] > df_label_all[x,names(g)[i]],"blue","red")
  FeaturePlot(tiss,features = x,order =TRUE) + labs(color = "Expression") + labs(title = x,subtitle = subtitle) + 
    theme(
      plot.title = element_text(face="bold", size = 30,color = color_label),
      plot.subtitle = element_text(size = 20),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15),
      axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks=element_blank(),
      axis.line = element_blank())
  # + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
pl = pl[order(seq(length(g))%%2,decreasing = TRUE)]
pl[[1]] = pl[[1]] + labs(y = "Favored by LMD") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "red"))
pl[[(length(pl)/2)+1]] = pl[[(length(pl)/2)+1]] + labs(y = "Favored by Other methods") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "blue"))

@@

<!--   ## Gene-gene distance(similarity)--------- -->
<!--   distance_method = "jaccard" -->
<!--   clustering_method = "average" -->
<!--   dist = Calculate_distance(dat_alra[local_gene,], method = distance_method) -->

@@

<!--   p_heatmap = pheatmap(as.matrix(dist), -->
<!--                 annotation_col = annotation_df, -->
<!--                 cluster_rows = gene_hree, -->
<!--                 cluster_cols = gene_hree, -->
<!--                 treeheight_row = 0, -->
<!--                 annotation_colors = ann_colors,  -->
<!--                 col=colorRampPalette(c("red","white","blue4"))(99), -->
<!--                 show_colnames = FALSE, -->
<!--                 show_rownames = FALSE, -->
<!--                 annotation_legend = TRUE, -->
<!--                 silent = TRUE) -->
<!--   pl_module = FeaturePlot_meta(dat,visual_space,gene_partition) -->
<!--   legend <- get_legend(pl_module[[1]]) -->
<!--   prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = ceiling(length(pl_module)/2)) -->

@@

```{r}
consortium = "tabular_muris"
dir.path <- file.path(dir.path0,"LMD_data")
pl = lapply(c("marrow_facs","lung_facs","pancreas_facs"),function(tissue_name){
score_measure = read.table(file.path(dir.path,"benchmark",consortium,paste0(tissue_name,"_DI.csv")),header = TRUE)
score_measure$Method = ifelse(score_measure$Method %in% names(method_fullname),method_fullname[score_measure$Method],score_measure$Method)

@@

# Add null distribution
null_score_measure =
  read.table(file.path(dir.path,"benchmark",consortium,paste0(tissue_name,"_DI_null.csv")),header = TRUE)
# Calculate the mean & Prediction Interval
## account for both the variability of the observations and the uncertainty in estimating the mean
null_stats <- null_score_measure %>%
  group_by(TopGene) %>% 
  summarize(Mean = mean(DensityIndex),Sd = sd(DensityIndex),sample_size = n(),.groups = 'drop') %>%
  mutate( Lower_CI = Mean + qt(0.025, df = sample_size - 1) * Sd * sqrt(1 + 1 / sample_size), Upper_CI = Mean + qt(0.975, df = sample_size - 1) * Sd * sqrt(1 + 1 / sample_size) )
null_stats$'Method' = "Null"

@@

# SupFig - Sensitivity Test
## kNN
```{r}
folder.path = file.path(dir.path,"LMD_data",consortium,"intermediate_data", tissue_name, "sensitivity_test")
test_para = "knn"

@@

# fig = fig1 + fig2 + plot_annotation(title = "Sensitivity Test: Different kNN", theme = theme(plot.title = element_text(size = 20)))
# ggsave(filename = file.path(figure_path,"supfig-sensitivityknn.png"), plot = fig, width = 16, height = 5)
```
## PC
```{r}
folder.path = file.path(dir.path,"LMD_data",consortium,"intermediate_data", tissue_name, "sensitivity_test")
test_para = "pc"

@@

# SupFig-CellType-specific Module (Bone marrow)
## Jaccard Index Heatmap
```{r}
consortium = "tabular_muris"
tissue_name = "marrow_facs"
dir.path <- file.path(dir.path0,"LMD_data")
folder.path = file.path(dir.path,consortium)

@@

colnames(jaccard_index_pruned) = gsub("Module","M",colnames(jaccard_index_pruned))
jaccard_index_pruned = jaccard_index_pruned[names(sort(apply(jaccard_index_pruned,1,which.max))),]
p1 = Visualize_jaccard_mtx(jaccard_index_pruned, threshold = thred)
p1 = as.ggplot(p1) + coord_fixed()
```
##  Module-CT-TSNE
For each cell type, select the most specific modules for visualization (maximum jaccard index)
```{r}
pl_ct = lapply(colnames(one_hot_matrix),function(ct){
  FeaturePlot_custom(coord = Embeddings(tiss[["tsne"]]),value = as.character(one_hot_matrix[,ct]), title_name = ct, value_name = "Indicator") + scale_color_manual(values = c("0" = "lightgrey", "1" = scales::hue_pal()(1)))
})
names(pl_ct) = colnames(one_hot_matrix)

>>>>

---
title: "Paper_Figure"
author: "Ruiqi Li"
output: pdf_document
date: '2023-10-16'
---
# Load Data & Preprocess
```{r}
library("Seurat")
library("RColorBrewer")
library("dplyr")
library("patchwork")
library("ggplot2")
library("ggsignif")
library("LocalizedMarkerDetector")
source("paper_figure_function.R", echo = F)
source("paths.R")
figure_path = file.path(dir.path0,"figures")
dir.create(figure_path,recursive = TRUE)
setwd(figure_path)
```

# SupFig - Bone Marrow Cell Embedding
```{r}
dir.path <- dir.path0
data_source = "tabular_muris"
folder.path <- file.path(dir.path,data_source)
tissue_name = "marrow_facs"
tiss <- readRDS(file.path(folder.path,paste0(tissue_name,".rds")))
cell_label = tiss$cell_ontology_class
coldef = setNames(colorRampPalette(brewer.pal(12, "Paired"))(length(unique(cell_label))),unique(cell_label))
p1 = DimPlot(tiss, group.by = "cell_ontology_class",label = FALSE, cols = coldef) + guides(color = guide_legend(ncol = 1,override.aes = list(size = 3))) + labs(title = NULL)

@@

# Fig - Pipeline
```{r}
dir.path <- dir.path0
data_source = "tabular_muris"
folder.path <- file.path(dir.path,data_source)
tissue_name = "marrow_facs"
tiss <- readRDS(file.path(folder.path,paste0(tissue_name,".rds")))
W <- readRDS(file.path(folder.path,"intermediate_data",tissue_name,paste0(tissue_name,"_knn_graph.rds")))
res <- readRDS(file.path(folder.path,"intermediate_data",tissue_name,paste0(tissue_name,"_lmd_profile.rds")))
P_ls <- readRDS(file.path(folder.path,"intermediate_data",tissue_name,paste0(tissue_name,"_diffused_graph.rds")))
rho <- readRDS(file.path(folder.path,"intermediate_data",tissue_name,paste0(tissue_name,"_gene_distribution.rds")))
```
```{r}
# Plot knn graph
p = VisualizeGraph(affinity_m = W, layout = Embeddings(tiss[["tsne"]])) + NoLegend()
ggsave(filename = file.path(figure_path,"fig-pipeline1.png"), plot = p, width = 5, height = 5, dpi = 300)
```
```{r}
# Check Diffusion KL pattern for several genes
# good gene: Igll1,Fcnb # garbage marker: Fkbp1b, Tnks1bp1, Magi2,Uchl4
genes = c("Igll1","Tnks1bp1") 
# genes_label = c("localized","non_localized")
check_time = c(0,2^3,2^9,2^14)
p = VisualizeScorePattern(res$score_profile/res$score_profile$max_score0, genes = genes, add_point = check_time) + guides(linetype = "none")

@@

ggsave(filename = file.path(figure_path,"fig-pipeline2.png"), plot = p, width = 8, height = 5)
```
```{r}
# Check Gene Diffusion on Cell graph by time
pl = lapply(1:length(genes),function(i){
  gene = genes[i]
  VisualizeDiffusion(coord = Embeddings(tiss[["tsne"]]),init_state = rho[gene,,drop = FALSE],P_ls = P_ls,W = W,check_time = check_time,gene_name = NULL, gene_color = scales::hue_pal()(length(genes))[i])
})
p = as.ggplot(pl[[1]]) / as.ggplot(pl[[2]] & labs(title = NULL))
ggsave(filename = file.path(figure_path,"fig-pipeline3.png"), plot = p, width = 16, height = 8)
```

# Fig - the AUROC given the rank and the ground truth
```{r}
method_ls = c("lmd","haystack","hotspot","marcopolo","semi","wilcox_no_filter","hvg")
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v4","HVGs"),method_ls)
```
```{r}
dir.path <- dir.path0
data_source = "tabular_muris"
tissue_name = "marrow_facs"
folder.path = file.path(dir.path,"benchmark")
```
```{r}
# Define Full name
tissue_ls = list("tabular_muris" = c("marrow_facs","pancreas_facs","lung_facs"),
                 "azimuth" = c("human_kidney", "human_bone_marrow", "human_pancreas", "mouse_motor_cortex", "human_lung_hlca", "human_motor_cortex"))
data_source_full_name = c("tabular_muris" = "Tabular Muris","azimuth" = "Azimuth")
tissue_full_name = lapply(unlist(tissue_ls),function(i){
  tmp_name = 
  if(grepl("marrow",i)){tmp_name = "Bone Marrow"}
  else if(grepl("lung_hlca",i)){tmp_name = "Lung v2 (HLCA)"}
  else if(grepl("lung",i)){tmp_name = "Lung"}
  else if(grepl("pancreas",i)){tmp_name = "Pancreas"}
  else if(grepl("kidney",i)){tmp_name = "Kidney"}
  else if(grepl("motor_cortex",i)){tmp_name = "Motor Cortex"}
  else{tmp_name = NA}
  tmp_name
})
names(tissue_full_name) = unlist(tissue_ls)
tissue_full_name = unlist(lapply(1:length(tissue_full_name),function(i){
  ori_name = names(tissue_full_name)[i]
  if(grepl("_facs|mouse",ori_name)){
    tmp_name = paste0("Mouse-\n",tissue_full_name[i])
  }
  else if(grepl("human",ori_name)){
    tmp_name = paste0("Human-\n",tissue_full_name[i])
  }
  else{
    tmp_name = tissue_full_name[i]
  }
  tmp_name
}))
names(tissue_full_name) = unlist(tissue_ls)
```
```{r}
df_auc = do.call(rbind,
                lapply(1:length(tissue_ls),function(i){
                  df_all = NULL
                  for(j in tissue_ls[[i]]){
                    df = read.table(file.path(folder.path, names(tissue_ls)[i],paste0(j,"_auroc.csv")),header = TRUE)
                    df$'Tissue' = j
                    df_all = rbind(df_all,df)
                  }
                  df_all$'data_source' = names(tissue_ls)[i]
                  df_all}))
df_auc$Method = method_fullname[df_auc$Method]
df_auc = df_auc %>% filter(gt_set %in% c("CellMarkerDB","Top100"))
# Order Method based on mean AUROC
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("CellMarkerDB","Top100"))
levels(df_auc$gt_set) = c("Criterion1-\n CellMarkerDB","Criterion2-\n MaxFC")
df_auc$Tissue = tissue_full_name[df_auc$Tissue]
df_auc$data_source = data_source_full_name[df_auc$data_source]
df_auc$data_source = factor(df_auc$data_source, levels = data_source_full_name)
```
## Figure
```{r}
coldef = setNames(
  colorRampPalette(brewer.pal(8, "Set1"))(length(method_fullname)),
  method_fullname)

fig <- ggplot(df_auc, aes(x = Tissue, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") + facet_grid(gt_set~data_source, scales = 'free') +
  geom_text(aes(label = round(AUROC, 3)), position = position_dodge(width = 1), vjust = -0.25, size = 2.5, angle = 45) +
  labs(x = "Tissue", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method])

@@

ggsave(filename = file.path(figure_path,"fig-known_marker_comparison.png"), plot = fig, width = 12, height = 6)
```
## Table
```{r}
library("reshape2")
wide_data = df_auc; wide_data$AUROC = round(wide_data$AUROC,3)
wide_data <- reshape2::dcast(wide_data, gt_set + Tissue + data_source ~ Method, value.var = "AUROC")
colnames(wide_data)[1:3] = c("Criterion","Tissue","DataSource")
wide_data[,1:3] = wide_data[,3:1]; colnames(wide_data)[1:3]=colnames(wide_data)[3:1]
wide_data <- wide_data[order(wide_data$DataSource,wide_data$Tissue,wide_data$Criterion),]
wide_data[,1:3] = apply(wide_data[,1:3],2,function(x) gsub("[\n]|Criterion1-|Criterion2-","",x))
wide_data[,1:2] = apply(wide_data[,1:2],2,function(x) {x[duplicated(x)] = "";x})
wide_data$Tissue[17] = "Motor Cortex(Mouse)"
wide_data$Tissue[13] = "Motor Cortex(Human)"
wide_data$Tissue = gsub("Human-|Mouse-","",wide_data$Tissue)
# calculate average
avg_tmp = wide_data %>%
    group_by(Criterion) %>%
    summarize(across(3:(ncol(wide_data)-1), ~ round(mean(.x, na.rm = TRUE), 3)))
avg_tmp$DataSource = c("Average",""); avg_tmp$Tissue = "-"
wide_data = rbind(wide_data,avg_tmp)
bold_max <- function(vec) {
  max_val <- max(vec, na.rm = TRUE)
  vec = unlist(ifelse(vec == max_val, paste0("\\textbf{", vec, "}"), vec))
  return(vec)
}
wide_data[,4:ncol(wide_data)] = t(apply(wide_data[,4:ncol(wide_data)],1,bold_max))
wide_data[is.na(wide_data)] = "-"

write.csv(wide_data, file = file.path(folder.path,"AUROC_table.csv"), row.names = FALSE)
```
# SupFig-RunTime
```{r}
df_runtime = do.call(rbind,
                lapply(1:length(tissue_ls),function(i){
                  df_all = NULL
                  for(j in tissue_ls[[i]]){
                    df = read.table(file.path(folder.path, names(tissue_ls)[i],paste0(j,"_runtime.csv")),header = TRUE)
                    df$'Tissue' = j
                    df_all = rbind(df_all,df)
                  }
                  df_all$'data_source' = names(tissue_ls)[i]
                  df_all}))
df_runtime$Method = method_fullname[df_runtime$Method]
df_runtime$Tissue = tissue_full_name[df_runtime$Tissue]
df_runtime$data_source = data_source_full_name[df_runtime$data_source]
```
## Figure
```{r}
coldef = setNames(
  colorRampPalette(brewer.pal(8, "Set1"))(length(method_fullname)),
  method_fullname)

@@

# Fig - Gene Ranking Comparisons between LMD and Other Methods
```{r}
dir.path <- dir.path0
data_source = "tabular_muris"
tissue_name = "marrow_facs"
df_benchmark = read.table(file.path(dir.path,"benchmark", data_source, paste0(tissue_name,"_benchmark_rank_table.csv")),header = TRUE)
rownames(df_benchmark) = df_benchmark$gene
tiss = readRDS(file.path(dir.path,data_source, paste0(tissue_name,".rds")))
method_vs = "lmd"
method_vs_set = c("wilcox_no_filter","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
# df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
#   paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
# })
g = c("Cd19","Naaa","Mogat2","Grina","Abca13","Zf12","Il2rb","Phgdh","Vpreb2","Fyb")
names(g) = rep(method_vs_set,each = 2)
pl = lapply(1:length(g),function(i){
  x = g[i]
  subtitle = sprintf("%s:%d, %s:%d",method_fullname[method_vs],df_label_all[x,method_vs],method_fullname[names(g)[i]],df_label_all[x,names(g)[i]])
  color_label = ifelse(df_label_all[x,method_vs] > df_label_all[x,names(g)[i]],"blue","red")
  FeaturePlot(tiss,features = x,order =TRUE) + labs(color = "Expression") + labs(title = x,subtitle = subtitle) + 
    theme(
      plot.title = element_text(face="bold", size = 30,color = color_label),
      plot.subtitle = element_text(size = 20),
      legend.title = element_text(size = 20),
      legend.text = element_text(size = 15),
      axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks=element_blank(),
      axis.line = element_blank())
  # + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
pl = pl[order(seq(length(g))%%2,decreasing = TRUE)]
pl[[1]] = pl[[1]] + labs(y = "Favored by LMD") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "red"))
pl[[(length(pl)/2)+1]] = pl[[(length(pl)/2)+1]] + labs(y = "Favored by Other methods") + theme(axis.title.y = element_text(size = 20,face="bold", colour = "blue"))

@@

<!--   ## Gene-gene distance(similarity)--------- -->
<!--   distance_method = "jaccard" -->
<!--   clustering_method = "average" -->
<!--   dist = CalculateGeneDistance(dat_alra[local_gene,], method = distance_method) -->

@@

<!--   p_heatmap = pheatmap(as.matrix(dist), -->
<!--                 annotation_col = annotation_df, -->
<!--                 cluster_rows = gene_hree, -->
<!--                 cluster_cols = gene_hree, -->
<!--                 treeheight_row = 0, -->
<!--                 annotation_colors = ann_colors,  -->
<!--                 col=colorRampPalette(c("red","white","blue4"))(99), -->
<!--                 show_colnames = FALSE, -->
<!--                 show_rownames = FALSE, -->
<!--                 annotation_legend = TRUE, -->
<!--                 silent = TRUE) -->
<!--   pl_module = CustomModulePlot(dat,visual_space,gene_partition) -->
<!--   legend <- get_legend(pl_module[[1]]) -->
<!--   prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = ceiling(length(pl_module)/2)) -->

@@

```{r}
data_source = "tabular_muris"
dir.path <- dir.path0
pl = lapply(c("marrow_facs","lung_facs","pancreas_facs"),function(tissue_name){
score_measure = read.table(file.path(dir.path,"benchmark",data_source,paste0(tissue_name,"_DI.csv")),header = TRUE)
score_measure$Method = ifelse(score_measure$Method %in% names(method_fullname),method_fullname[score_measure$Method],score_measure$Method)

@@

# Add null distribution
null_score_measure =
  read.table(file.path(dir.path,"benchmark",data_source,paste0(tissue_name,"_DI_null.csv")),header = TRUE)
# Calculate the mean & Prediction Interval
## account for both the variability of the observations and the uncertainty in estimating the mean
null_stats <- null_score_measure %>%
  group_by(TopGene) %>% 
  summarize(Mean = mean(DensityIndex),Sd = sd(DensityIndex),sample_size = n(),.groups = 'drop') %>%
  mutate( Lower_CI = Mean + qt(0.025, df = sample_size - 1) * Sd * sqrt(1 + 1 / sample_size), Upper_CI = Mean + qt(0.975, df = sample_size - 1) * Sd * sqrt(1 + 1 / sample_size) )
null_stats$'Method' = "Null"

@@

# SupFig - Sensitivity Test
## kNN
```{r}
folder.path = file.path(dir.path,data_source,"intermediate_data", tissue_name, "sensitivity_test")
test_para = "knn"

@@

# fig = fig1 + fig2 + plot_annotation(title = "Sensitivity Test: Different kNN", theme = theme(plot.title = element_text(size = 20)))
# ggsave(filename = file.path(figure_path,"supfig-sensitivityknn.png"), plot = fig, width = 16, height = 5)
```
## PC
```{r}
folder.path = file.path(dir.path,data_source,"intermediate_data", tissue_name, "sensitivity_test")
test_para = "pc"

@@

# SupFig-CellType-specific Module (Bone marrow)
## Jaccard Index Heatmap
```{r}
data_source = "tabular_muris"
tissue_name = "marrow_facs"
dir.path <- dir.path0
folder.path = file.path(dir.path,data_source)

@@

colnames(jaccard_index_pruned) = gsub("Module","M",colnames(jaccard_index_pruned))
jaccard_index_pruned = jaccard_index_pruned[names(sort(apply(jaccard_index_pruned,1,which.max))),]
p1 = Visualize_jaccard_mtx(jaccard_index_pruned, threshold = thred)
p1 = as.ggplot(p1) + coord_fixed()
```
##  Module-CT-TSNE
For each cell type, select the most specific modules for visualization (maximum jaccard index)
```{r}
pl_ct = lapply(colnames(one_hot_matrix),function(ct){
  CustomFeaturePlot(coord = Embeddings(tiss[["tsne"]]),value = as.character(one_hot_matrix[,ct]), title_name = ct, value_name = "Indicator") + scale_color_manual(values = c("0" = "lightgrey", "1" = scales::hue_pal()(1)))
})
names(pl_ct) = colnames(one_hot_matrix)
